Results

### 2019-06-27 analysis/03_analysis.Rmd
All the things (draws)

# Load data
# results <- readRDS(here("data", "derived_data", "results.rds"))
```

@@

>>>>

intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 1 # + Demographics

# Load and extract data and model output (see model-calibration.R)
if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.RDS"))
if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
if (social_views == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
if (public_political == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
if (public_political_social == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
data <- run$data
fit <- run$fit
```

@@

# Model checking

```{r model-checking}
source(here::here("R", "stan_utility.R"))

# Check for divergences
check_div(fit)

# # Check the effective sample size (not working for a hierarchical model?)
# check_n_eff(fit)
# 
# # Check the Rhat statistic (not working for a hierarchical model?)
# check_rhat(fit)

# Check trace plots (SUBSET?)
fit %>%
  extract(
    inc_warmup = TRUE,
    permuted = FALSE
  ) %>%
  mcmc_trace(
    regex_pars = "Theta",
    n_warmup = 1000,
    facet_args = list(
      nrow = round((data$L * data$C)/7), 
      labeller = label_parsed
    )
  )

# ggsave(
#   "intercept_trace_noncentered.png",
#   path = here::here("analysis", "output", "figures"),
#   width = 12, height = 6, units = "in"
# )
```

# Extract draws

```{r extract-draws}
# Extract posterior draws
draws <- fit %>% 
  spread_draws(Theta[i, j]) %>% 
  ungroup() %>% 
  filter(.iteration > 500)

# Save draws
if (intercept == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept_noncentered.rds"))
if (public_affairs == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))
if (political_ideology == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "political_ideology.rds"))
if (social_views == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "social_views.rds"))
if (charity_voluntarism == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds"))
if (demographics == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "demographics.rds"))
if (public_political == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political.rds"))
if (public_political_social == 1)  write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social.rds"))
if (public_political_social_charity == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity_demo.rds"))
```

# Plot marginals

```{r plot-marginals}
# Plot marginals
level_labels <- c(
  str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
  str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
  "Financial transparency: Yes",
  "Accountability: Yes",
  str_c("Funding sources: ", c("Funded primarily by a handful of wealthy private donors", "Funded primarily by government grants")),
  str_c("Relationship with host government: ", c("Criticized by government", "Under government crackdown"))
)

# Covariates...

draws %>% 
  mutate(
    levels = factor(
      i,
      labels = level_labels
    )
  ) %>%
  ggplot(aes(x = Theta, y = levels)) + 
  geom_halfeyeh(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Attribute Levels")

# Save plot
ggsave(
  "intercept_marginal-posteriors_noncentered.png",
  path = here::here("analysis", "output", "figures"),
  width = 12, height = 6, units = "in"
)
```
